Macro Impacts

### 2016-08-01 Macro Impacts Revised.tex
Whoops! Transmission+Reflection fixed

A(t+\delta t) = A(t)e^{K\f{\delta t}{Q(r(t)}}\,.

@@

@@

@@

Suppose now that the macros impact the earth from all directions with equal likelihood. Consider any one of these macros. It sees a line, and it has equal likelihood of being any distance away from the origin. Now, since each point on the line exists as part of a circular cross-section, the associated distance has weight $2\pi R_{\te{Earth}}$. That's it! Hence, if $A_D$ is a finite set of detectible area measurements over $D = \{D_i:D_i\in[0,R_\te{Earth}],i\in\{1,\dots,N\}\}$. Assuming $D_i - D_{i+1}$ is fixed for all $i$, and that $D_N\approx R_{\te{Earth}}$ and $D_1 \approx 0$, then $A=\f{\sum_i A_{D_i}D_i}{\sum_i D_i}$ is the average detectable surface area. In the continuous case, this turns into the obvious integral.

>>>>

A(t+\delta t) = A(t)e^{K\f{\delta t}{Q(r(t))}}\,.

@@

\td{A}{t}{}&= A(t)e^{-K\f{t}{Q(r(t))}}\lim_{\delta t\to 0}\f{e^{K\f{t +\delta t}{Q(r(t))}}-{e^{K\f{t}{Q(r(t))}}}}{\delta t}\,,\\

@@

We begin with an amplitude $A(k,t)$, a function of amplitude and wave number, gotten from the Fourier decomposition of the source. Since the source depends on the wave vector, it is important to use spherical coordinates in phase space. It may be reasonable to just use the first order terms in $k$ since the lunar seismometers measure from  0.004 Hz to 2 Hz. However, second and third order terms may be desirable, given that signifiant portions of the measurable range lie at order unity. These are gotten by selectively truncating the hypergeometric series in section 2.

@@

Suppose now that the macros impact the earth from all directions with equal likelihood. Consider any one of these macros. It sees a line, and it has equal likelihood of being any distance away from the origin. Now, since each point on the line exists as part of a circular cross-section, the associated distance has weight $2\pi R_{\te{Earth}}$. That's it! Hence, if $A_D$ is a finite set of detectible area measurements over $D = \{D_i:D_i\in[0,R_\te{Earth}],i\in\{1,\dots,N\}\}$. Assuming $D_i - D_{i+1}$ is fixed for all $i$, and that $D_N\approx R_{\te{Earth}}$ and $D_1 \approx 0$, then 
\begin{align}
A=\f{\sum_i A_{D_i}D_i}{\sum_i D_i}\,,
\end{align}
is the average detectable surface area. In the continuous case, this turns into the obvious integral.
